%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{johan andreas}{ Versteegh}{Sensor Mechatronics Creator} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Koppelsedijk 18
4191LC
Nederland
~
Mob: +31(0)627042986
~
\href{mailto:johan@techplaygroup.com}{johan@techplaygroup.com}
\href{http://www.techplaygroup.com}{www.techplaygroup.com}
% \href{http://facebook.com/johnsmith}{fb://jsmith}
\section{languages}
dutch
norvegian
english
german
french
\section{skills}
{\color{red} $\varheartsuit$} Mechatronics
Python, C++, PHP
CSS3 \& HTML5
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2001--2002}
%{Elektrotechniek {\normalfont (parttime)}}
{Engineering and Life Sciences {\normalfont (parttime)}}
% {Hogeschool van Arnhem en Nijmegen}
{HAN University of Applied Sciences, Arnhem}
{Upgrading my electronics skills}
%------------------------------------------------
\entry
{1994--2000}
%{Industrieel Ontwerpen}
{Industrial Design}
{TU Delft}
{Specialization in Commerce}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

%\section{experience}
\sectionlang{english}{experience}
\sectionlang{nl}{werkervaring}

\begin{entrylist}
%------------------------------------------------
\entry
{2011--2013}
{INCAS³}
%{Assen, Nederland}
{Assen, Netherlands}
{Industrial Researcher} \\
\lang{nl}{Incas3 is een onafhankelijk non-profit research instituut dat zich bezig houdt met het oplossen van uitdagende problemen binnen de industrie en op sociaal technisch gebied.
Functie:
Het ontwikkelen en inkopen van test opstellingen om de door de wetenschappers gevonden theorieën te bewijzen.
Interim Head of engineering.
Industrial Researcher: de schakel vormen tussen de wetenschap en de industrie en in dat proces de daaruit voortkomende (deel)oplossingen proberen om te zetten naar produceerbare eindproducten.
Projecten:
SPRINT, SMARTBOT, SENSOR CITY, MoreWise. 
Binnen deze projecten was een van mijn taken de Phd’s en Master studenten op technisch vlak te begeleiden.}
\\
Detailed achievements:
\begin{itemize}
\item Learned how to make amazing coffee
\item Finally determined the reason for \textsc{PC LOAD LETTER}:
\begin{itemize}
\item Paper jam
\item Software issues:
\begin{itemize}
\item Word not sending the correct data to printer
\item Windows trying to print in letter format
\end{itemize}
\item Coffee spilled inside printer
\end{itemize}
\item Broke the office record for number of kitten pictures in cubicle
\end{itemize}}
%------------------------------------------------
\entry
{2010--2011}
{LEHMAN BROTHERS}
{London, United Kingdom}
{\emph{Summer Intern} \\
Rated "truly distinctive" for Analytical Skills and Teamwork.}
%------------------------------------------------
\entry
{2008-2009}
{Buy More}
{Burbank, California}
{\emph{Computer Repair Specialist} \\
Worked in the Nerd Herd and helped to solve computer problems by asking customers to turn their computers off and on again.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2011}
{Postgraduate Scholarship}
{School of Business, The University of California}
{Awarded to the top student in their final year of a Bachelors degree.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{communication skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2011}
{Oral Presentation}
{California Business Conference}
{Presented the research I conducted for my Masters of Commerce degree.}
%------------------------------------------------
\entry
{2010}
{Poster}
{Annual Business Conference, Oregon}
{As part of the course work for BUS320, I created a poster analyzing several local businesses and presented this at a conference.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data analysis, company profiling, risk analysis, economics, web design, web app creation, software design, marketing \textbf{personal:} piano, chess, cooking, dancing, running

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}

\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

\printbibsection{book}{books} % Print all books from the bibliography

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
\end{refsection}

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
\end{refsection}

\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

% Sections, subsections, subsubsections:

\sectionlang{no}{norksidoo} % in the first parameter you can freely use
                            % both short or long language codes
\sectionlang{english}{Section 1}

% Strings that are displayed only in a certain language
\lang{nl}{hier dus nederlands}
\lang{en}{This string shows up only in English.}
\lang{no}{Og denne på norsk.}


\end{document}